Towards Semantic Patches

### 2010-06-18 papers/MIPS2010/abstract.tex
Exemple, le fichier stlc2.ga beautified
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@110 403e655e-980a-47bd-8c60-1ee5348bb6b7

\newcommand{\sort}{\textsf{s}}
\newcommand{\gor}{\ |\ }
\newcommand{\gdecl}[2]{{#1}\ &::=\ {#2}}
\newcommand{\subst}[2]{\{#1/#2\}}

@@

%\newcommand{\remplan}[1]{}
%\newcommand{\remtext}[1]{}

@@

>>>>

\newcommand{\sort}{\textsf{s}}
\newcommand{\gor}{\ |\ }
\newcommand{\gdecl}[2]{{#1}\ &::=\ {#2}}
\newcommand{\subst}[2]{\{#1/#2\}}
\newcommand{\nat}{\mathbb N}

@@

%\renewcommand{\remplan}[1]{}
%\renewcommand{\remtext}[1]{}

@@

\paragraph{Example}

Here is a well-typed repository describing the simply-typed
$\lambda$-calculus and constructing two $\lambda$-terms sharing some
sub-derivations: 
{\small
\begin{align}&
(\nat : *).
(o : \nat).
(s : \nat \to \nat).
(type : *).
(base : type).
(arr : type \to type \to type). \\&
(env : *).
(nil : env).
(cons : type \to env \to env). \\&
(term : *).
(var : \nat \to term).
(lam : term \to term).
(app : term \to term \to term). \\&
(lookup : env \to \nat \to type \to *).
(lookup_o : (e : env).(a : type).(f = cons\ a\ e : env). lookup\ e\ o\ a). \\&
(lookup_s : (e : env).(a b : type).(n : \nat).(sn = s\ n : \nat).(f =
cons\ a\ e : env). lookup\ e\ n\ b \to lookup\ f\ sn\ b). \\&
(of : env \to term \to type \to *). \\&
(of_v : (e : env).(a : type).(n : \nat).(v = var\ n : term).
          lookup\ e\ n\ a \to of\ e\ v\ a). \\&
(of_l : (e : env).(t : term).(a\ b: type).(c = arr\ a\ b : type).
          (u = lam\ t : term).(f = cons\ a\ e : env).
          of\ f\ t\ b \to of\ e\ u\ c). \\&
(of_a : (e : env).(t\ u: term).(a\ b: type).
          (c = arr\ a\ b : type).(v = app\ t\ u : term).
          of\ e\ t\ c \to of\ e\ u\ a \to of\ e\ v\ b). \\&
(1 = s\ o : \nat).(v_0 = var\ o : term).(v_1 = var\ 1 : term).
(t_3 = lam\ v_0 : term).(ch_0 = lam\ t_3 : term).\\&
(t_1 = app\ v_0\ v_1 : term).(t_2 = lam\ t_1 : term).
(t_4 = lam\ t_2 : term).
(bb = arr\ base\ base : type). \\&
(e_0 = cons\ bb\ nil : env).
(e_1 = cons\ base\ e0 : env).
(d_0 = lookup_o\ e_1\ base : lookup\ e_1\ o\ base). \\& %        (* a→a, a ⊢ 0 : a *)
(d_1 = of_v\ e_1\ base\ o\ d0 : of\ e_1\ v_0\ base). %	   (* a→a, a ⊢ 0 : a *)
(d_2 = of_l\ e_0\ v_0\ base\ base d_1 : of\ e_0\ t_3\ bb). \\& %   (* a→a ⊢ λ0 : a → a *)
(bbb = arr\ bb\ bb : type).
(d_3 = of_l\ nil\ t_3\ bb\ bb\ d_2 : of\ nil\ ch_0\ bbb). \\& %  (* ⊢ λλ0 : (a→a)→(a→a) *)
(g_1 = lookup_o\ e_0\ bb : lookup\ e_0\ o\ bb).
(g_2 = lookup_s\ e_0\ base\ bb\ o\ g_1 : lookup\ e_1\ 1\ bb). \\&
(g_3 = of_v\ e_1\ bb\ 1\ g_2 : of\ e_1\ v_1\ bb).	          % (* a→a, a ⊢ 1 : a→a *)
(t_5 = app\ v_1\ v0 : term). \\&
(g_4 = of_a\ e_1\ v_1\ v_0\ base\ base\ g_3\ d_1 : of\ e1\ t5\ base). % (* ... ⊢ 1 0 : a *)
(t_6 = lam\ t_5 : term). \\&
(g_5 = of_l\ e_0\ t_5\ base\ base\ g_4 : of\ e_0\ t_6\ bb).  %  (* a→a ⊢ λ(1 0) : a→a *)
(t_7 = lam\ t_6 : term).
(g_6 = of_l\ nil\ t_6\ bb\ bb\ g_5 : of\ nil\ t_7\ bbb). *	 %  (* ⊢ λλ(1 0) : (a→a)→a→a  *)
\end{align}
}
